Discrete Quantum Theories and Computing

### 2018-12-30 dissertation.tex
dissertation.lyx  "Chapter 1 Introduction" Updating...

Although it is convenient to assume physical quantities is as continuous
as their mathematical models, each physical quantity discussed in
the previous paragraph could not have a simple one-to-one correspondence
with a real number. Chuang-tzu's stick are made by molecules and cannot
be cut in halves endlessly. The input charge of an integrator must
actually be an integer multiple of the elementary charge. A prefect
square cannot be draw physically. Even we don't draw it, but merely
ask whether it exists in the space. This question is still beyond
our ability to answer because whether the space itself is ultimately
discrete or continuous is still an unsolved question. Even if a prefect
square exists physically, we may not able to decide whether the ``square''
we discussed is really prefect or almost prefect differing only by
an arbitrarily small extent. Similar situation applying to the length
of a slide rule, it is beyond our ability to decide whether its length
is ultimately discrete or continuous. Even if its length is continuous,
identifying which real number represents its length requires infinite
precision, but the precision in reality is limited generally three
or four significant figures~\cite{wiki:AnalogComputer}. As the results,
even if analog computers really store real numbers, they cannot be
precisely read, written, and used to branch the computation. The opposite
of the last statement is sometimes assumed by real computational models.
For example, Blum, Cucker, Shub, and Smale modeled their BCSS machine
to allow the operations of deciding whether a number is greater or
equal to zero over real numbers and whether a number is exactly zero
over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
Hence, when the quantities used to branch the computation is closed
to zero, the branch chosen by a BCSS machine cannot reliably predict
the branch chosen by a realistic analog computer. Since two branches
of computations may not have any relations, the follow-up computational
paths may be significantly different, and these difference may not
be compensated by error analysis techniques easily like the butterfly
effect. Therefore, the computational power of analog computers might
be far weaker than the prediction based on this kind of theoretical
models.%
\begin{comment}
\todo{Maybe extended to consider probabilistic model? }
\end{comment}

@@

\centering{}\centering{}%
\begin{tabularx}{\linewidth}{ccYY}
\toprule 
\addlinespace
Physical quantities & Discrete & Discrete with extreme small unit & Continuous?\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational devices & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Mathematical representation & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational model  & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & 
Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
Not reliably, because precision can never be high enough, and the difference between their computational power might not be able compensated by error analysis techniques. \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Inspired quantum models &  & Quantum Theories and Computing over Finite Fields & Quantum Interval-Valued Probability Measures (QIVPM)\tabularnewline\addlinespace
\addlinespace
\bottomrule
\end{tabularx}
\end{sidewaystable}
The situations for classical quantities and the computational power
above them are summarized in Table~\ref{tab:Comparison}, and the
two possibilities dealing with real-valued models inspires us two
types of quantum models. Similar to classical analog computers, the
quantum circuit model, the most widely used model of quantum computing,
manipulates quantities which are not discrete apparently: the probability
amplitudes of quantum states. To address the similar inconsistency,
we first review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
amplitudes are in the field of complex numbers. If the probability
amplitudes are assumed to be ultimately discrete, we replace the field
of complex numbers by discrete finite fields and consider the quantum
theories and computing over finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
and \ref{chap:DQT=000026DQC}. Another possibilities could be that
the probability amplitudes would never be quantized no matter how
hard we try. Notice that the probability amplitudes can never be accessed
directly in an experiment, the accessible properties of a quantum
system is its measurement results and the probability of an event.
Hence, to incorporate the finite precision measurement into the quantum
theory, we consider a framework called quantum interval-valued probability
measures (QIVPM) in Chapter~\ref{chap:QIVPM}.

>>>>

Although it is convenient to assume physical quantities is as continuous
as their mathematical models, each physical quantity discussed in
the previous paragraph could not have a simple one-to-one correspondence
with a real number. Chuang-tzu's stick are made by molecules and cannot
be cut in halves endlessly. The input charge of an integrator must
actually be an integer multiple of the elementary charge. A prefect
square cannot be draw physically. Even we don't draw it, but merely
ask whether it exists in the space. This question is still beyond
our ability to answer because whether the space itself is ultimately
discrete or continuous is still an unsolved question. Even if a prefect
square exists physically, we may not able to decide whether the ``square''
we discussed is really prefect or almost prefect differing only by
an arbitrarily small extent. Similar situation applying to the length
of a slide rule, it is beyond our ability to decide whether its length
is ultimately discrete or continuous. Even if its length is continuous,
identifying which real number represents its length requires infinite
precision, but the precision in reality is limited generally three
or four significant figures~\cite{wiki:AnalogComputer}. As the results,
even if analog computers really store real numbers, they cannot be
precisely read, written, and used to branch the computation. The opposite
of the last statement is sometimes assumed by real computational models.
For example, Blum, Cucker, Shub, and Smale modeled their BCSS machine
to allow the operations of deciding whether a number is greater or
equal to zero over real numbers and whether a number is exactly zero
over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
Hence, when the quantities used to branch the computation closes to
zero, the branch chosen by a BCSS machine cannot reliably predict
the branch chosen by a realistic analog computer. Since two branches
of computations may not have any relations, the follow-up computational
paths may be significantly different, and these difference may not
be compensated by error analysis techniques easily like the butterfly
effect. Therefore, the computational power of analog computers might
be far weaker than the prediction based on this kind of theoretical
models.%
\begin{comment}
\todo{Maybe extended to consider probabilistic model? }
\end{comment}

@@

\centering{}\centering{}%
\begin{tabularx}{\linewidth}{ccYY}
\toprule 
\addlinespace
Physical quantities & Discrete & Discrete with extreme small unit & Continuous, but unlikely to verify they really are\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational devices & Digital computer & Analog computer & Analog computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Mathematical representation & Integers & Real numbers & Real numbers\tabularnewline\addlinespace
\addlinespace
\addlinespace
Computational model  & Turing machine & BCSS machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & 
Not reliably, but after we have a better technology to manipulate the minimum units, we can predict the physical phenomenon and their computational power by a better discrete model. & 
Not reliably, because precision can never be high enough, and the difference between their computational power might not be able compensated by error analysis techniques. \tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Inspired quantum models &  & Quantum Theories and Computing over Finite Fields & Quantum Interval-Valued Probability Measures (QIVPM)\tabularnewline\addlinespace
\addlinespace
\bottomrule
\end{tabularx}
\end{sidewaystable}
The situations for classical quantities and the computational power
above them are summarized in Table~\ref{tab:Comparison}, and the
two possibilities dealing with real-valued models inspires us two
types of quantum models. Similar to classical analog computers, the
quantum circuit model, the most widely used model of quantum computing,
manipulates quantities which are not discrete apparently: the probability
amplitudes of quantum states. To address the similar inconsistency,
we first review the ``conventional quantum theory''\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.} in Chapter~\ref{chap:Conventional-Quantum-Theory}, where the probability
amplitudes are in the field of complex numbers. If the probability
amplitudes are assumed to be ultimately discrete, we replace the field
of complex numbers by discrete finite fields and consider the quantum
theories and computing over finite fields in Chapter~\ref{chap:Unrestricted-Finite-Fields}
and \ref{chap:DQT=000026DQC}. Another possibilities could be that
the probability amplitudes would never be quantized no matter how
hard we try. Notice that the probability amplitudes can never be accessed
directly in an experiment, the accessible properties of a quantum
system is its measurement results and the probability of an event.
Hence, to incorporate the finite precision measurement into the quantum
theory, we assume the probability of an event

, and consider a framework called quantum interval-valued probability
measures (QIVPM) in Chapter~\ref{chap:QIVPM}.
